Trawl Summary

### 2022-06-17 sub-projects/trawl/trawl_README.Rmd
workflow redo fixed links for new workflow.
Big commit. Updated qD models and plots. work on manuscript to finalize results

---
title: "Trawl-README"
author: "JRJ"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) { 
      out_dir <- "docs";
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(here::here(), out_dir, 'trawl_README.html')) })
output: 
  html_document:
      keep_md: true
      toc: true
      toc_float: true
      toc_depth: 3
      numbered_sections: true
---

@@

1. "packages.R"
2. "datascript.R" (sourcing this document will call the 'packages.R' script)
3. "trawl_rarefaction.R"
4. "trawl_specaccum.R"

>>>>

---
title: "Trawl-README"
author: "JRJ"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) { 
      out_dir <- here::here("sub-projects/trawl/docs");
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(here::here(), out_dir, 'trawl_README.html')) })
output: 
  html_document:
      keep_md: true
      toc: true
      toc_float: true
      toc_depth: 3
      numbered_sections: true
---

@@

1. "packages.R"
2. "datascript.R" (sourcing this document will call the 'packages.R' script)
3. "analyze_rarefaction.R"
4. "trawl_specaccum.R"
5. "analyze_hill_diversity.R"

### 2022-06-17 sub-projects/trawl/trawl_summary.Rmd
Big commit. Updated qD models and plots. work on manuscript to finalize results

---
title: 'Trawl Summary'
author: "Jim Junker"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) { 
      out_dir <- './docs';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'trawl_summary.html')) })
output: 
  html_document:
      keep_md: true
      toc: true
      toc_float: true
      toc_depth: 3
      numbered_sections: true
---

@@

<!-- # These data vary in coverage and are being updated: -->
<!-- #  -->
<!-- # `r knitr::include_graphics("./figures/env_facet_plot.png")` -->

@@

date_lists = TB_trawl_commonsite %>%
  named_group_split(date_id) %>%
  map(., ~.x %>% select(-year, -month,-date_id))

beta_lists <- lapply(date_lists, function(x,r){ betapart::beta.temp(x = x, y = r, index.family = 'jaccard')}, x = date_lists[[1]]) 
beta_dates <- gsub('^([0-9]{4}-)([0-9]{1})$', '\\10\\2', names(beta_lists))
beta_df <- bind_rows(beta_lists) %>% mutate(Date = as.Date(paste0(beta_dates,"-01"), "%Y-%m-%d")) %>% #select(Date, everything()) %>%
  pivot_longer(-Date, names_to = "partition", values_to = "value")

rich_time <- 
  ggplot(TB_time_df, aes(x = Date, y = richness, group = data_type)) +
  geom_point(aes(colour = data_type),size = 1.5) +
  geom_line(aes(colour = data_type),size = 1.2) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
  scale_y_continuous(name = "Species Richness")+
  scale_colour_manual(name = "", values = viridis(4)[c(2,3)]) +
  theme_minimal() +
  theme(legend.position = c(0, 1), legend.justification = c(0, 1), legend.background = element_rect(fill = "transparent", colour = NA),
        axis.title.x = element_blank(), axis.text.x = element_blank(),
        legend.spacing.y = unit(-0.1, 'cm'))

 jaccard_time <-
  ggplot(beta_df, aes(x = Date, y = value, group = partition)) + 
   geom_point(aes(colour = partition), size = 1.5) +
  geom_line(aes(colour = partition), size = 1.2) +
  scale_y_continuous(name = "Jaccard dissimilarity", limits = c(0,1.1), expand = c(0.01,0.01))+
  scale_colour_manual(name = "", values = viridis(7)[c(2,4,7)], labels = c("jaccard", "nestedness","turnover")) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
   theme_minimal() +
  theme(legend.background = element_rect(colour = NA, fill = 'transparent'),
        legend.position = c(0,1), legend.justification = c(0,1), axis.title.x = element_blank(),
        legend.spacing.y = unit(-0.2, 'cm'))

grid.arrange(rich_time, jaccard_time, ncol = 1)

>>>>

---
title: 'Trawl Summary'
author: "Jim Junker"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) { 
      out_dir <- here::here('sub-projects/trawl/docs');
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(out_dir, 'trawl_summary.html')) })
output: 
  html_document:
      keep_md: true
      toc: true
      toc_float: true
      toc_depth: 3
      numbered_sections: true
---

@@

<!-- # These data vary in coverage and are being updated: -->
<!-- #  -->
<!-- # `r knitr::include_graphics(here::here("sub-projects/trawl/docs/figures/env_facet_plot.png"))` -->

@@

# date_lists = TB_trawl_commonsite %>%
  # named_group_split(date_id) %>%
#   map(., ~.x %>% select(-year, -month,-date_id))
# 
# beta_lists <- lapply(date_lists, function(x,r){ betapart::beta.temp(x = x, y = r, index.family = 'jaccard')}, x = date_lists[[1]]) 
# beta_dates <- sapply(as.numeric(names(beta_lists)), function(x) as.Date(x, origin = as.Date("2007-01-01"))) 
# beta_df <- bind_rows(beta_lists) %>% mutate(Date = as.Date(paste0(beta_dates,"-01"), "%Y-%m-%d")) %>% #select(Date, everything()) %>%
#   pivot_longer(-Date, names_to = "partition", values_to = "value")
# 
# rich_time <- 
#   ggplot(TB_time_df, aes(x = Date, y = richness, group = data_type)) +
#   geom_point(aes(colour = data_type),size = 1.5) +
#   geom_line(aes(colour = data_type),size = 1.2) +
#   scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
#   scale_y_continuous(name = "Species Richness")+
#   scale_colour_manual(name = "", values = viridis(4)[c(2,3)]) +
#   theme_minimal() +
#   theme(legend.position = c(0, 1), legend.justification = c(0, 1), legend.background = element_rect(fill = "transparent", colour = NA),
#         axis.title.x = element_blank(), axis.text.x = element_blank(),
#         legend.spacing.y = unit(-0.1, 'cm')) 
# 
#  jaccard_time <-
#   ggplot(beta_df, aes(x = Date, y = value, group = partition)) + 
#    geom_point(aes(colour = partition), size = 1.5) +
#   geom_line(aes(colour = partition), size = 1.2) +
#   scale_y_continuous(name = "Jaccard dissimilarity", limits = c(0,1.1), expand = c(0.01,0.01))+
#   scale_colour_manual(name = "", values = viridis(7)[c(2,4,7)], labels = c("jaccard", "nestedness","turnover")) +
#   # scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
#    theme_minimal() +
#   theme(legend.background = element_rect(colour = NA, fill = 'transparent'),
#         legend.position = c(0,1), legend.justification = c(0,1), axis.title.x = element_blank(),
#         legend.spacing.y = unit(-0.2, 'cm')) 
#    
#  
# grid.arrange(rich_time, jaccard_time, ncol = 1)
